Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-10 paper.qmd
obstacles and attempt at looping the gif

Methods
- motus in R
- Shiny (show default app, super simple examples of each thing (not using bird data)) (basically a Shiny tutorial)
- leaflets (big tools that we will be using for this specific app)
- (shiny live (you can start with static images))

Results
- code

@@

![Deployments map](deploy.gif){.lightbox}

@@

### <em>Winter Roosting</em>
<p>The next page is the <em>Winter Roosting> page. On the first tab of this page, <em>Map</em>, there is a leaflet map. The blue markers are of each winter location that birds have roosted. The circle and cluster markers are for the individual birds who spent the winter there. The user can choose which year of winter they want to look at (the months defined for winter roosting for this application are January, February, and December) and the default is all years. On the second tab of this page, <em>Roosting Group</em>, there is another leaflet map which tracks the birds from the same roosting location based on year and location. </p>

@@

### <em>About</em>
<p>The <em>About</em> includes page includes three tabs: <em>Abstract</em>, <em>Data</em>, and <em>Adirondack Deployments</em>. The <Abstract> tab simply includes the abstract for this project. The <em>Data</em> tab includes a data table for all of the Evening Grosbeak data used for these visualizations. The <em>Adirondack Deployments</em> tab includes a data table specfically for all of the Evening Grosbeak data from birds that were deployed from the Adirondack Region.</p>

@@

>>>>

@@

![Deployments map](output-onlinegiftools.gif){.lightbox}

@@

### <em>Winter Roosting</em>
<p>The next page is the <em>Winter Roosting</em> page. On the first tab of this page, <em>Map</em>, there is a leaflet map. The blue markers are of each winter location that birds have roosted. The circle and cluster markers are for the individual birds who spent the winter there. The user can choose which year of winter they want to look at (the months defined for winter roosting for this application are January, February, and December) and the default is all years. On the second tab of this page, <em>Roosting Group</em>, there is another leaflet map which tracks the birds from the same roosting location based on year and location. </p>

@@

### <em>About</em>
<p>The <em>About</em> includes page includes three tabs: <em>Abstract</em>, <em>Data</em>, and <em>Adirondack Deployments</em>. The <Abstract> tab simply includes the abstract for this project. The <em>Data</em> tab includes a data table for all of the Evening Grosbeak data used for these visualizations. The <em>Adirondack Deployments</em> tab includes a data table specifically for all of the Evening Grosbeak data from birds that were deployed from the Adirondack Region.</p>

@@

### Obstacles
<p>Creating the Shiny App for this large dataset provided many hurdles with data manipulation and programming. One problem occurred with Shiny and reactive data. For the deployments page, the cluster/circle markers for each bird will only show up if this ta comes absolutely first in the app structure. This was a problem as we wanted to restructure the app and have the interactive deployments map later, but we had to leave it first to keep our data displayed. Another problem was also related to the reactive data on the deployments page: no other tab could have this type of reactive data that was observing events. On the deployments map, as a user clicks on a marker, the app observes this event and stores the data for the next tab. The original plan was to have a similar mechanism for the winter roosting locations map. But, when attempting to make observable clicks on this map, the deployments map data would disappear. The intended mecahnism for this was replaced in the winter groups map by adding a dropdown menu for location: not quite as fluid, but still makes it possible for a user to look through the routes of a specific wintering group. </p>

### Future and Improvements
